### 2017-08-30 Sections/economics_of_the_quantum_internet.tex
Minor updates. Author update

We will now treat some of these economic issues in the context of a global network of unified quantum computing resources, which are then equitably time-shared\index{Time-sharing}. We argue in Sec.~\ref{sec:quant_ec_lev} that this time-shared model for quantum computation is always more computationally efficient than having distinct quantum computers operating independently in parallel, owing to the super-linear scaling in their joint computational power.

@@

Let $t$ be the classical-equivalent runtime\index{Classical-equivalent power} of a quantum algorithm comprising $n$ qubits. We define a \textit{computational scaling function}\index{Computational scaling functions} characterising this relationship,

@@

The exact form of the scaling function will be specific to the algorithm being deployed, and the computational model (e.g cluster states vs the circuit model, as well as choices in error correction, amongst other factors).

%
% Virtual Scaling Function
%

@@

Until now we have characterised the entire network by a single scaling function. Of course, the scaling functions observed by different market participants needn't all be the same, as they are functions of not only the hardware, but also the participants' different algorithmic applications.

Consider taking a single unit of time (i.e we are ignoring cost discounting over multiple units of time) and dividing it amongst a number of nodes, $n_\text{nodes}$, each with their own scaling function, $f_\text{sc}^{(i)}$. The total classical-equivalent runtime of the computation is additive, given simply by a linear combination of the classical-equivalent processing times of the individual node. This yields the relationship for combining scaling functions,
\begin{definition}[Combined scaling functions]\index{Combined computational scaling functions}\label{def:comb_sc_func}
The effective combined computational scaling function, $f_\text{sc}^\text{(joint)}$, of a group of participants, each with their own scaling functions, $f_\text{sc}^{(i)}$, is given by,
\begin{align}
	t_\text{joint} &= \sum_{i=1}^{n_{\text{nodes}}} \beta_i \cdot f_\text{sc}^{(i)}(n_\text{global}) \nonumber \\
	&= f_\text{sc}^\text{(joint)}(n_\text{global}),
\end{align}
where $\beta_i$ characterise the share of processing time allocated to each node, and for normalisation,
\begin{align}
\sum_{i=1}^{n_\text{nodes}} \beta_i = 1.
\end{align}

@@

We make several assumptions about the efficiency of the quantum marketplace. These are largely based on the conventional efficient-market hypothesis (EMH)\index{Efficient-market hypothesis (EMH)} \cite{???}.

@@

\begin{postulate}[Efficient markets]\label{post:market_eff}\index{Efficient markets} We make the following efficiency assumptions on the dynamics of the quantum marketplace:
\begin{itemize}
	\item Qubits are a `scarce' resource --- there is always positive, non-zero demand for them.
	\item No wastage --- quantum computational resources are always fully utilised, with no down-time.
	\item Transaction free --- transaction costs are negligible.
	\item Negligible cost-of-carry --- e.g storage and maintenance costs are negligible.
	\item High liquidity --- it is always possible to execute transactions at market rates.
	\item Perfect price competition --- there is sufficient competition that profits from quantum hardware and the execution of quantum computations is marginal.
	\item Arbitrage-free --- market rates for different assets and derivatives are perfectly consistent, with no opportunity for `free money' by trading on market discrepancies.
	\item Perfect information --- all market participants have complete knowledge of all market variables, including one another.
	\item Rational markets --- all market participants act rationally\footnote{i.e with perfect economic self-interest --- \textit{Avaritia}.} upon available information.
	\item Indefinite lifetime --- there is no deterioration or death of quantum hardware over time.
\end{itemize}
\end{postulate}

@@

Now, if \mbox{$Q=1$} we have the breakeven point, whereby investment into physical hardware is profit-neutral in payback. If \mbox{$Q<1$} we spend more on hardware than we gain from its use. But if \mbox{$Q>1$} we can make guaranteed profit by investing in new hardware. The perfect price competition assumption (Pos.~\ref{post:market_eff}) will drive the market price towards the zero-profit breakeven point (but not quite -- someone has to make money!), such that \mbox{$Q\gtrapprox 1$}. That is, the economic gain approximates the hardware investment,
\begin{align} \label{sec:gain_eq_invest}
	n_\text{gain}(t) \gtrapprox n_\text{invest}(t).
\end{align}

>>>>

We will now treat some of these economic issues in the context of a global network of unified quantum computing resources, which are then equitably time-shared\index{Time-sharing}. We argue in Sec.~\ref{sec:quant_ec_lev} that this time-shared model for quantum computation is always more computationally efficient than having distinct quantum computers operating independently in parallel, owing to the super-linear scaling in their joint computational power. While this section provides mathematical details of various economic models, Sec.~\ref{sec:economics} provides a popular, high-level discussion of these issues.

@@

Let $t$ be the classical-equivalent runtime\index{Classical-equivalent power} of a quantum algorithm comprising $n$ qubits -- that is, how long would a given classical computer require to implement this $n$-qubit quantum computation? We define a \textit{computational scaling function}\index{Computational scaling functions} characterising this relationship,

@@

The exact form of the scaling function will be specific to the algorithm being deployed\footnote{For example, the \textit{circuit depth}, i.e number of gate applications in series, will heavily influence the number of classical steps required to simulate the circuit.}, and the computational model (e.g cluster states vs the circuit model, as well as choices in error correction, amongst other factors). Most notably, different quantum algorithms offer different scalings in their quantum speedup -- Grover's algorithm offers only a quadratic quantum speedup, compared to the exponential speedup afforded by Shor's algorithm. Thus, the computational scaling function depends on both the hardware and software.

%
% Virtual Scaling Functionx
%

@@

Until now we have characterised the entire network by a single scaling function. Of course, the scaling functions observed by different market participants needn't all be the same, as they are functions of not only the hardware, but also the participants' different algorithmic applications (i.e software).

Consider taking a single unit of time (i.e we are ignoring cost discounting over multiple units of time) and dividing it amongst a number of nodes, $n_\text{nodes}$, each with their own scaling function, $f_\text{sc}^{(i)}$. The total classical-equivalent runtime of the computation is additive, given simply by a linear combination of the classical-equivalent processing times of the individual nodes. This yields the relationship for combining scaling functions,
\begin{definition}[Combined scaling functions]\index{Combined computational scaling functions}\label{def:comb_sc_func}
The effective combined computational scaling function, $f_\text{sc}^\text{(joint)}$, of a group of participants, each with their own scaling functions, $f_\text{sc}^{(i)}$, is given by,
\begin{align}
	t_\text{joint} &= \sum_{i=1}^{n_{\text{nodes}}} \beta_i \cdot f_\text{sc}^{(i)}(n_\text{global}) \nonumber \\
	&= f_\text{sc}^\text{(joint)}(n_\text{global}),
\end{align}
where $\beta_i$ characterise the share of processing time allocated to each node, and for normalisation,
\begin{align}
\sum_{i=1}^{n_\text{nodes}} \beta_i = 1.
\end{align}

@@

We make several assumptions about the efficiency of the quantum marketplace. These are largely based on the conventional efficient-market hypothesis (EMH)\index{Efficient-market hypothesis (EMH)} \cite{???}, readily taught in undergraduate ECON101 and subsequently summarily rejected upon entering ECON202. For ease of exposition, we will remain in the ECON101 classroom.

@@

\begin{postulate}[Efficient markets]\label{post:market_eff}\index{Efficient markets} We make the following efficiency assumptions on the dynamics of the quantum marketplace:
\begin{itemize}
	\item Qubits are a `scarce' resource --- there is always positive, non-zero demand for them.\index{Scarce resource}
	\item No wastage --- quantum computational resources are always fully utilised, with no down-time.\index{Wastage}
	\item Transaction free --- transaction costs are negligible.\index{Transaction cost}
	\item Negligible cost-of-carry --- e.g storage and maintenance costs are negligible.\index{Cost-of-carry}
	\item High liquidity --- it is always possible to execute transactions at market rates.\index{Liquidity}
	\item Perfect price competition --- there is sufficient competition that profits from quantum hardware and the execution of quantum computations is marginal.\index{Price competition}
	\item Arbitrage-free --- market rates for different assets and derivatives are perfectly consistent, with no opportunity for `free money' by trading on market discrepancies.\index{Arbitrage-free}
	\item Perfect information --- all market participants have complete knowledge of all market variables, including one another.\index{Perfect information}
	\item Rational markets --- all market participants act rationally\footnote{i.e with perfect economic self-interest --- \textit{Avaritia}.} upon available information.\index{Rational markets}
	\item Indefinite asset lifetime --- there is no deterioration or death of quantum hardware over time.\index{Asset lifetime}
\end{itemize}
\end{postulate}

@@

Now, if \mbox{$Q=1$} we have the breakeven point, whereby investment into physical hardware is profit-neutral in payback. If \mbox{$Q<1$} we spend more on hardware than we gain from its use and run at a loss. But if \mbox{$Q>1$} we can make guaranteed profit by investing in new hardware. The perfect price competition assumption (Pos.~\ref{post:market_eff}) will drive the market price towards the zero-profit breakeven point (but not quite -- someone has to make money!), such that \mbox{$Q\gtrapprox 1$}. That is, the economic gain approximates the hardware investment,
\begin{align} \label{sec:gain_eq_invest}
	n_\text{gain}(t) \gtrapprox n_\text{invest}(t).
\end{align}

### 2017-08-30 Sections/mathematical_representation_of_quantum_networks.tex
Minor updates. Author update

%
% Network Costs & Attributes
%

@@

\begin{definition}[Network cost metrics] \label{def:metric} Cost metrics satisfy the properties:\index{Network cost metrics}
	\begin{itemize}
    	\item Identity operations: If a channel performs nothing, its associated cost is zero, \mbox{$c(\mathbb{\hat{I}}) = 0$}.
    	\item Triangle inequality: \\ $c(v_1\to v_2\to v_3) \leq c(v_1\to v_2) + c(v_2\to v_3)$, \\ across all paths \mbox{$v_1 \to v_2 \to v_3$}.
    	\item Positivity: \mbox{$c\geq 0$}. This ensures that shortest-path algorithms will function correctly.
	\end{itemize}
\end{definition}
Attributes, on the other hand do not have a distance interpretation, and may have arbitrary structure. A detailed discussion on the relationship between costs and attributes is presented in Sec.~\ref{sec:c_vs_a}.

@@

A \textit{route}\index{Routes} between two nodes, Alice ($A$) and Bob ($B$), of the network, $G$, is an acyclic subgraph connecting those nodes, \mbox{$R_{A\to B}\subseteq G$}. In general ad hoc networks there will typically be multiple paths between two nodes \mbox{$A\to B$}. For a particular cost metric, the cost of an entire route is simply the sum of the costs of each of the constituent links,
\begin{definition}[Route costs]
The net cost of a route \mbox{$A\to B$}, traversing nodes $v_i$, is,
\begin{align}\index{Route costs}
c(R_{A\to B}) = \sum_{i=1}^{|R_{A\to B}|-1} c(v_i \to v_{i+1}),
\end{align}
where $v_i$ is the $i$th node in the route $R_{A\to B}$.
\end{definition}

>>>>

%
% Cost Vector Analysis
%

@@

\begin{definition}[Network cost metrics] \label{def:metric} Cost metrics satisfy the properties:\index{Network cost metrics}
	\begin{itemize}
    	\item Identity operations: If a channel performs nothing, its associated cost is zero, \mbox{$c(\mathbb{\hat{I}}) = 0$}.
    	\item Triangle inequality: \\ $c(v_1\to v_2\to v_3) \leq c(v_1\to v_2) + c(v_2\to v_3)$, \\ across all paths \mbox{$v_1 \to v_2 \to v_3$}. In the case of strict equality under addition we refer to the cost as a \emph{strictly additive cost}.
    	\item Positivity: \mbox{$c\geq 0$}. This ensures that shortest-path algorithms will function correctly. It is also congruent with the intuitive expectation that data traversing a communications channel is not somehow better off than if it hadn't traversed that channel at all.
	\end{itemize}
\end{definition}
Attributes, on the other hand do not have a distance interpretation, and may have arbitrary structure. A detailed discussion on the relationship between costs and attributes is presented in Sec.~\ref{sec:c_vs_a}.

@@

A \textit{route}\index{Routes} between two nodes, Alice ($A$) and Bob ($B$), of the network, $G$, is an acyclic subgraph connecting those nodes, \mbox{$R_{A\to B}\subseteq G$}. In general ad hoc networks there will typically be multiple paths between two nodes \mbox{$A\to B$}. For a particular cost metric, the cost of an entire route is simply the sum of the costs of each of the constituent links,
\begin{definition}[Route costs]
The net cost of a route \mbox{$A\to B$}, using cost metric $c(A\to B)$, traversing nodes $v_i$, is,
\begin{align}\index{Route costs}
c(R_{A\to B}) = \sum_{i=1}^{|R_{A\to B}|-1} c(v_i \to v_{i+1}),
\end{align}
where $v_i$ is the $i$th node in the route $R_{A\to B}$.
\end{definition}
